

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
# TODO: which further dependencies needed?
#source("_setup.R") # I get an error message...
esti_dir <- "//gaia/fme/home/ralpers/public/estimands_in_ml_files"
rwd_dir <- file.path(esti_dir, "real_world_data")
library(dplyr)
library(knitr)
library(ggplot2)
library(tidyr)

R <- readr::read_csv(file.path(rwd_dir, "sim_results", "results.csv"),
                  show_col_types = FALSE)
```


# Perfromance metrics per fold
```{r}
metrics <- R %>% 
  group_by(missing, split_type, outcome, method, hp, iter) %>% 
  summarise(sensitivity = sum(y == 1 & yhat == 1)/sum(y == 1),
            specificity = sum(y == 0 & yhat == 0)/sum(y == 0),
            balanced_accuracy = mean(c(sensitivity, specificity)))

min_max_performance <- metrics %>% 
  group_by(missing, split_type, outcome, method) %>% 
  summarise(min_sensitivity = min(sensitivity, na.rm = T),
            max_sensitivity = max(sensitivity, na.rm = T),
            NA_sensitivity = sum(is.na(sensitivity)),
            min_specificity = min(specificity, na.rm = T),
            max_specificity = max(specificity, na.rm = T),
            NA_specificity = sum(is.na(specificity)),
            min_balanced_accuracy = min(balanced_accuracy, na.rm = T),
            max_balanced_accuracy = max(balanced_accuracy, na.rm = T))

kable(min_max_performance)
```
There is enough predictive power in the features that there is no systematic majority vote in the models using the different types of data, splits, outcomes and methods.
In three countries nobody was reported do be dead after 14 days and in 2 of them there was even nobody reported dead after 6 months.

# Balanced accuracy

```{r}
ba_per_job <- metrics %>% group_by(missing, split_type, outcome, method, hp) %>% 
  summarize(mean_across_folds = mean(balanced_accuracy, na.rm = T),
            var_between_folds = var(balanced_accuracy, na.rm = T))
#kable(ba_per_job)

```

## Summarizing results of different hyperparameters
```{r}
ba_across_hp <- ba_per_job %>% group_by(missing, split_type, outcome, method) %>% 
  summarize(mean_across_hp = mean(mean_across_folds, na.rm = T),
            var_between_hp_mean_across_folds = var(mean_across_folds),
            mean_across_hp_var_between_folds = mean(var_between_folds),
            var_between_hp_var_between_folds = var(var_between_folds))
#kable(ba_across_hp)
```
### Outcome 1: death within 14 days
```{r}
plot_ba_ID14 <- ggplot(filter(ba_per_job, outcome == "ID14"), aes(x = split_type, y = mean_across_folds)) +
  geom_boxplot() +
  facet_wrap(method~missing)
plot_ba_ID14
```

### Outcome 2: death within 6 months
```{r}
plot_ba_FDEAD <- ggplot(filter(ba_per_job, outcome == "FDEAD"), aes(x = split_type, y = mean_across_folds)) +
  geom_boxplot() +
  facet_wrap(method~missing)
plot_ba_FDEAD
```

## Pairwise difference between results of different hyperparameters
```{r}
ba_diff_per_job <- ba_per_job %>% group_by(missing, outcome, method, hp) %>%
  summarize(ran_geo = mean_across_folds[split_type == "cv_10_a"] - mean_across_folds[split_type == "country_diff"],
            ran_temp = mean_across_folds[split_type == "cv_10_a"] - mean_across_folds[split_type == "year_lag1"],
            temp_geo = mean_across_folds[split_type == "year_lag1"] - mean_across_folds[split_type == "country_diff"]) %>% 
  pivot_longer(c(ran_geo, ran_temp, temp_geo), names_to = "compared_split_types", values_to = "diff_mean_ba")

overall_difference <- ba_diff_per_job %>% group_by(compared_split_types, method) %>% 
  summarize(mean_diff = mean(diff_mean_ba),
            var_diff = var(diff_mean_ba),
            min_diff = min(diff_mean_ba),
            max_diff = max(diff_mean_ba))
kable(overall_difference)
```

### Outcome 1: death within 14 days
```{r}
plot_diff_ba_ID14 <- ggplot(filter(ba_diff_per_job, outcome == "ID14"), aes(x = compared_split_types, y = diff_mean_ba)) +
  geom_boxplot() +
  facet_wrap(method~missing)
plot_diff_ba_ID14
```

### Outcome 2: death within 6 months
```{r}
plot_diff_ba_FDEAD <- ggplot(filter(ba_diff_per_job, outcome == "FDEAD"), aes(x = compared_split_types, y = diff_mean_ba)) +
  geom_boxplot() +
  facet_wrap(method~missing)
plot_diff_ba_FDEAD
```
